Political Support in the United States

### 2024-03-16 paper/paper.qmd
Update paper.qmd

format: pdf
number-sections: true
bibliography: references.bib
---

@@

# Results {#sec-results}
Our results are summarized in @tbl-model-summary-table.Logistic regression is a common classification algorithm used to predict binary classification problems. In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function. When interpreting the results of logistic regression models. Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature. The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.

>>>>

format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Results {#sec-results}
Our results are summarized in @tbl-model-summary-tableLogistic regression is a common classification algorithm used to predict binary classification problems. In logistic regression, the probability that a sample belongs to a certain class is determined by mapping the input data to a probability range between 0 and 1 using a logical function, such as the sigmoid function. When interpreting the results of logistic regression models. Logistic regression models can provide coefficients (or weights) for each feature variable that represent the relative importance of the feature. The positive and negative symbols of the coefficient can tell us whether the feature has positive or negative influence on the target category, and the absolute value of the coefficient can map the importance of the feature to the target category.
